---
title: "Football Scores"

author: 
  - Rahul Gopeesingh
thanks: "Code and data are available at: https://github.com/Rahul-Uoft/Football-scores.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)



```




## Model set-up

Define $y_i$ as the number of goals a team scores in a game. Then $\lambda_i$ is the amount of possession they had   

\begin{align} 
y_i &\sim \mbox{Poisson}(\lambda_i) \\
\mu_i &= \alpha + \beta x \lambda_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We use a poisson model in this case due to the relationship being between one input and one output. The input variable is the possession and a team possesses the ball many times throughout a game whereas the output variable being the number of goals scored where the probability of a goal being scored in each possession is relatively small. We assume each goal scoring chance from possession is independent of each other and therefore this follows a binomial which can be approximated to the poisson.



```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)
setwd("/Users/rahulgopeesingh/Documents/Football scores")
#### Workspace setup ####
library(tidyverse)
library(rstanarm)
library(modelsummary)

#### Read data ####

### Model data ####
setwd("/Users/rahulgopeesingh/Documents/Football scores")

first_model <-
  readRDS(file = here::here("goals_rstanarm.rds"))



```


```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false


modelsummary(
  list(
    "Goals" = first_model
  )
)

```

